Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-29 writing/DraftExposurePaper/DraftExposurePaper.Rmd
unique fips for frances and allison

```{r eval = FALSE}
frances_wind <- read.csv("/Users/joshuaferreri/Documents/NWR_frances_wind.csv", 
                         na.strings = 999,
                         header = TRUE)
save(frances_wind, file = "writing/DraftExposurePaper/frances_wind.RData")
```

@@

```{r eval = FALSE}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
```
```{r}
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
```

>>>>

```{r eval = FALSE}
#frances_wind <- read.csv("/Users/joshuaferreri/Documents/NWR_frances_wind.csv", 
 #                        na.strings = 999,
  #                       header = TRUE)
#save(frances_wind, file = "writing/DraftExposurePaper/frances_wind.RData")
```

@@

```{r eval = FALSE}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
```
```{r}
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
```
```{r}
#Allison-2010
allison_fips <- allison_nldas$fips
allison_fips <- unique(allison_fips)
```
```{r}
#Frances-2004
frances_fips <- frances_nldas$fips
frances_fips <- unique(frances_fips)
```
